---
title: "DataScienceThruQuarto"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

### Data Science

Being a data scientist is mainly about turning raw information into easily visualized and pretty graphs and figures. Statisticians focus mainly only the more raw outputs but a **data scientist** should also be able to tell a good *story* with the information they have generated. The stories tend to be in the form of dry reports but the idea still stands. I lean mostly on the side of data scientist as I find that writing up reports to be the best part of dealing with data!

### Trying data processing

Using the iris dataset and trying out visualizing a specific vector

Computing kernel density of sepal length

```{r}
density(iris$Sepal.Length)
```

Set "y" as the density of sepal length

```{r}
y <- density(iris$Sepal.Length)
```

Determine the:

class of "y"

```{r}
class(y)
```

type of "y"

```{r}
typeof(y)
```

structure of "y"

```{r}
str(y)
```

Plot "y" and change the title and x-axis label

```{r}
#| echo: false
plot(y, main="Sepal Length", 
     xlab="Length in cm")
```
